Urbanization and Public Transportation of Los Angeles

### 2023-11-10 Paper.Rmd
label bus and rail

# Create the line plot
p <- ggplot(ridership_long, aes(x=Year, y=RateOfChange, color=Type, group=Type)) +
  geom_line() +
  scale_y_continuous(labels = label_comma()) +
  labs(title="Trend in Rate of Change of Public Transportation Usage",
       x="April of Each Year",
       y="Rate of Change in Total Monthly Ridership",
       color="Transportation Type") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(2019, 2023))

>>>>

# Create the line plot
p <- ggplot(ridership_long, aes(x=Year, y=RateOfChange, color=Type, group=Type)) +
  geom_line() +
  scale_y_continuous(labels = label_comma()) +
  labs(title="Trend in Rate of Change of Public Transportation Usage",
       x="April of Each Year",
       y="Rate of Change in Total Monthly Ridership",
       color="Transportation Type") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(2019, 2023)) +
  scale_color_discrete(labels=c("Bus", "Rail"))
